Inefficient Concessions and Mediation

### 2024-02-03 QJPS/Inefficient_Concessions.tex
Format and zip files for final submission to QJPS

Control of strategically valuable territory is often contested in both civil and interstate wars. Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide a military advantage in a future conflict. Following the 1992 war between Armenia and Azerbaijan over the disputed region of Ngorno-Karabakh, Armenia retained control of a significant amount of Azerbaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland. Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory. Thus, it might have been efficient in the mid-1990s for the Armenian/Karabakh side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence. However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor that connects Ngorno-Karabakh and Armenia. Azerbaijani control of the territory surrounding the corridor would empower Azerbaijan to seize military advantage in the future and cut off land travel between Ngorno-Karabakh and Armenia. The territory was not conceded, and the conflict persisted in a costly stalemate for almost twenty years until war broke out anew in 2020.

@@

\section{Appendix}

\subsection{Pooling equilibrium}
\begin{lemma}
	From Round 1 on, playing (Distrust,Distrust) in all rounds is a subgame perfect Nash equilibrium of the continuation game for both types regardless of beliefs.
	\label{lemma:1}
\end{lemma}
\emph{Proof}: As $D>0$ and $W>0$, the dominant stage game action for all types is to play Distrust. Thus, the stage game equilibrium is (Distrust,Distrust), and in any repeated game, playing the stage game equilibrium in each round is an equilibrium of the entire game. \hfill $\blacksquare$\\

That is, one high-type equilibrium strategy is to pool with the low types by always playing Distrust. If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays Distrust, then either type of player $i$ is made strictly better off by playing Distrust in each round given player $j$'s behavior. Given that the stage-game equilibrium will be (Distrust,Distrust), players have no incentive to give a concession in Period 0 because concessions are costly, and signaling one's type can give no benefit in this equilibrium. Types pool by never giving concessions and always playing Distrust.

\subsection{No-Concessions Separating Equilibrium}

 We examine the conditions for a separating equilibrium held in place by a grim trigger.

 \noindent{\emph{Proof of Proposition \ref{proposition:1}}:\\
Playing Trust in the first round and thereafter, as long as Trust has always been played, is incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first round and then every round thereafter by the one-shot deviation principle. If both countries play Trust in a round, a Cooperation equilibrium takes place, and both countries continue to play Trust in every round with the grim trigger threat of Distrust. Low types play Distrust in the first round, so a high type that observed Distrust being played would respond by playing Distrust in Round 2 and all future rounds. A country plays Trust if and only if the following condition is satisfied:
\begin{equation*}
  p\left(\frac{T}{1- \delta}\right) +(1-p)\left({-D}+\frac{\delta(W-D)}{1- \delta} \right)\geq p \left(T + W + \frac{\de}{1-\de}(W-D)\right) +(1-p)\frac{W-D}{1- \delta}.
\end{equation*}
Simplifying, we have
%\be
%  p\left(\frac{T}{1- \delta_h}\right) \geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)W
%\ee
\begin{equation*}
  pT \geq p \left((1-\de)(T + W) + \de (W-D)\right) + (1-\de)(1-p)W
\end{equation*}
\begin{equation*}
  pT \geq pT -p\de T +pW -p\de W + p \de W -p \de D  + W -\de W -pW + p\de W
\end{equation*}
\begin{equation*}
  p\de T +p \de D + \de W - p\de W  \geq W 
\end{equation*}
\be
	\delta \geq \frac{W}{(1-p)W + p(T+D)} = \de^{nc}.
	\label{eq:ncse}
\ee

If the potential advantages of Cooperation are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust. Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Distrust in each round even if the other country plays Trust. Thus, we call these countries low types for purposes of this equilibrium. \hfill $\blacksquare$

\subsection{Concessions Separating Equilibrium}

If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved in the absence of concessions in Period 0.\footnote{Countries need to deliver concessions in Period 0, not just promise them.} If, instead, two negotiating parties have sufficient incentive to give a concession in Period 0 that indicates they are capable of cooperation, these high types could safely play Trust in Round 1, allowing two high types to avoid the trap of the No Cooperation outcome that would occur under pooling.

Below are the details of the \emph{concessions separating equilibrium} analysis. We denote the equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type. These equilibrium gifts mean that when Round 1 is reached, countries know which type the other country is and play accordingly. The concessions phase acts as a coordination device to match countries' actions. For two countries of the same type to play different actions is an off-equilibrium contingency. These off-equilibrium payoffs are nonetheless necessary for calculating the minimum separating concession. 
\\
\\
\emph{Proof of Lemma~\ref{lemma:3}:}\\
In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on \emph{concessions separating equilibria} in which countries reveal their types truthfully. This allows high types to only play Trust in Round 1 with other high types and to play Distrust with low types. Low types play Distrust (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.

Though low types might be willing to give a non-zero gift in a separating equilibrium, they will only do this if it gives them some advantage. Here, high types only cooperate with other high types, so giving a concession cannot help low types to achieve a higher payoff in the repeated game. Because their concession $g_l$ enters negatively in the payoff function, low types' optimal concession is, therefore, 0.

High types have the incentive to play Trust only in the Cooperation equilibrium, which can only be sustained by a pair of high types. Both types benefit from the other country playing Trust, so all countries have an incentive to signal that they are high types if concessions are costless (cheap talk). Thus, costless announcements cannot lead to truthful revelation. If concessions are to lead to a separating equilibrium, they must be costly. \hfill $\blacksquare$
\\
\\
\emph{Proof of Proposition \ref{proposition:2}:}\\
In the separating equilibrium constructed here, players believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low-type gift. In this case, the binding incentive compatibility constraint is the low type IC constraint. When we set $g_l=0$ following Lemma~\ref{lemma:3}, the low-type IC constraint is\\  
\begin{equation*}
	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h.
\end{equation*}
This expression represents the low types' incentives for truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift. Simplifying this inequality, we see that the high types need to give a gift 
\be
	g_h \geq p(X_{FT}^l-X_{FF}^l)
	\label{eq:cse}
\ee 
in order to separate from the low type.

High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$. Because utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible while still achieving separation. This occurs when Expression~\ref{eq:cse} holds with equality. Substituting in from the definitions of $X_{FT}^l$ and $X_{FF}^l$ yields the minimum separating gift\footnote {Although not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made. Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils. Thus, a more powerful country would be more able to plunder and hence has to make a greater concession to convincingly convey that it is a high type.}
\be
	g_h^*=p(T+D).
	\label{eq:cse2}
\ee 
 To get the high types to send nonzero concessions, the high type incentive compatibility constraint must be satisfied. That is, the payoff from separating must be higher than the payoff from pooling with the low types: 
$$pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h.$$
In terms of fundamentals, we have
\be
	p\frac{T}{1-\de_h}+(1-p)\frac{W-D}{1-\de_h} - g_h \geq \frac{W-D}{1-\de_h}.
	\label{eq:cse3}
\ee
Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a \emph{concessions separating equilibrium} to exist:
\be
\delta_h \geq \frac{W}{T+D} = \de^c.
\ee
That is, we need the high types to have a sufficiently large discount factor. \hfill $\blacksquare$\\
\\
\emph{Proof of Corollary~\ref{corollary:1}:}\\
To show that the patience threshold for the \emph{no-concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption $T+D>W.$

We multiply both sides by $(1-p)>0$ and then subtract $p(T+D)$ from both sides to get
$$(T+D) > (1-p)W +p(T+D).$$
Because $0<p<1$ and $W$, $T$, and $D$ are all positive, both sides of the inequality are positive. Thus, we have
$$\de^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de^{c}.$$

In the case that both types of equilibria exist, i.e., $\de_h \geq \de^{nc}$, the high types prefer the \emph{no-concessions separating equilibrium} if and only if
\begin{equation*}
p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right) \geq p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - (1-p)g_h.
\end{equation*}
This simplifies to preferring the \emph{concessions separating equilibrium} if and only if
$$0 \geq (1-\de_h)W-p(1-\de_h)(T+D).$$
Rearranging, we have
\be
 p \geq \frac{W}{T+D}.
\ee
That is, the high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{T+D}$. \hfill $\blacksquare$

\subsection{Concessions with Material Value}
\label{ap:mat_val}
\emph{Proof of Proposition \ref{proposition:csemv}:}\\
In the separating equilibrium constructed in Proposition~\ref{proposition:csemv}, players believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low-type gift. In this case, the binding incentive compatibility constraint is the low type IC constraint. Taking account of the result of  Lemma~\ref{lemma:3} that $g_l=0$, we have
\begin{equation}
	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h.
	\label{eq:matval1}
\end{equation}
On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg_h$). Then (Distrust,Distrust) is played, and the payoffs depend on whether this low type faces a high or a low type because the implications for future material value are different. With probability $p$, the low type receives a gift and invests in the military. With probability $(1-p)$, neither side gives concessions. The left side of Expression~\ref{eq:matval1} is then $pg_h + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right]$.

On the right side, the low type gives and receives a gift from the high type with probability $p$. With probability $p$, this low type faces a high type who invests the gift in civil society. With probability $(1-p)$, the low type's gift goes to another low type who invests in the military, and the low type does not receive a gift. So the right hand side of Expression~\ref{eq:matval1} becomes $-g_h + pg_h + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)$.

Substituting into Expression~\ref{eq:matval1} and simplifying, we have
%\begin{multline*}
%	pg_1 + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right] \geq \\
%-g_1 + pg_1 + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)
%\end{multline*}
\begin{equation*}
	g_h + p(W+Wg_h-D) \geq p\left(T + Tg_h +W + Wg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
\end{equation*}
%\begin{equation*}
%	g_h - pD \geq p\left(T + Tg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
%\end{equation*}
\begin{equation*}
	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h\geq \left(1-\de_l\right)p\left(D +	 T\right).
\end{equation*}
We have assumed that $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D > 0$ so we can divide to get
%\begin{equation*}
%	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h \geq \left(1-\de_l\right)p\left(D +	 T\right)
%\end{equation*}
\begin{equation}
	g_h \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D} = g^1
	\label{eq:matval2}
\end{equation}

This implies that the high types need to give a gift at least as large as $g^1$ to separate from the low type; that is, if the high types give a gift smaller than $g^1$, a low type has the incentive to mimic the high type and the separating equilibrium is destroyed.

High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$. Because utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation. This occurs when Expression~\ref{eq:matval2} holds with equality. That is, the optimal high type gift in this equilibrium is $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.

The high-type incentive compatibility constraint must not be violated for high types to send nonzero concessions. That is, the payoff from separating must be higher than the payoff from not giving a gift and pooling with the low types. Note that if the high type pools with the low type, it knows it will play Distrust and so invests any concession received in military buildup. Therefore, the high-type IC constraint is
\begin{equation*}
	p\frac{T+Tg^1}{1-\de_h} + (1-p)\frac{W-D-Dg^1}{1-\de_h} - (1-p)g^1 \geq 
	p\frac{W+Wg^1-D}{1-\de_h} + (1-p)\frac{W-D}{1-\de_h} +pg^1.
\label{eq:matval3}
\end{equation*}

\noindent Simplifying, we have
$$p(T+Tg^1) + (1-p)(W-D-Dg^1)) - (1-\de_h)g^1 \geq p(W+Wg^1-D) + (1-p)(W-D)$$
%$$pT(1+g^1) - (1-p)Dg^1 - (1-\de_h)g^1 \geq p(W+Wg^1-D)$$
$$\de_h g^1 \geq p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1$$
%$$\de_h \geq \frac{p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1 }{g^1}$$
%$$\de_h \geq \frac{p(W-D-T) + pg^1 (W-T) + (1-p)Dg^1 + g^1 }{g^1}$$
$$\de_h \geq \frac{p(W-D-T)}{g^1} + p (W-T) + (1-p)D + 1.$$

Substituting the minimum efficient concession from Expression~\ref{eq:matval2}, we have the condition for a \emph{concessions separating equilibrium} to exist in terms of fundamentals:
\be
	\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1.
\ee
That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$

\vskip.3in
\noindent\emph{Comparative statics}

We start by examining the gifts in a \emph{concessions separating equilibrium}, first with no material value (or destroyed material value) and then when concessions have future material value.

It is direct that the gift in the {concessions separating equilibrium} with no material value (or destroyed material value) increases in $p$ because the gift is equal to $p(T+D)$. The gift also clearly increases in both $T$ and $D$.

It is straightforward that the gift in the model with material value, $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, increases in $p$. Recall that all the variables are assumed to be strictly positive, with $0 < \delta_l < 1$. It follows that the numerator increases in $p$ and the denominator decreases in $p$. Recall that we assume the denominator is positive. Therefore, $g^1$ increases in $p$. In formal terms, $\frac{\partial g^1}{\partial p} = \frac{(1 - \de_l +D)(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2} > 0$.

$g^1$ does not changed with $W$ because $W$ does not enter the expressing anywhere. The other three parameters require working out the formal result.

For the patience level of the low type: $$\frac{\partial g^1}{\partial \delta_l} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(-p)(T+D) - \left(1-\de_l\right)p\left(D + T\right)(-1)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$  $$= \frac{-\left(\left(1-\de_l\right)\left(1 - pT \right)p(T+D) + (1-p) D\right)p(T+D) + \left(1-\de_l\right)p\left(D +	 T\right)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$ $$= \frac{(1-p) pD(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term, so it is positive. Therefore we have $\frac{\partial g^1}{\partial \delta_l} > 0$.

For the benefit from negotiating partner playing Trust: 
$$\frac{\partial g^1}{\partial T} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(\de_l p -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 - pT + pD + pT\right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 + pD \right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term, so it is positive. Therefore we have $\frac{\partial g^1}{\partial T} > 0$.

For the damages from negotiating partner playing Distrust: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D - \left(D + T\right)(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) - T(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{1-\de_l -pT + \de_l p T - T +pT\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{1-\de_l + \de_l p T - T\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Because both the denominator and $(1-\de_l)p$ are strictly positive, the sign of this derivative matches the sign of $1-\de_l + \de_l p T - T$. It is positive when $\frac{1-\de_l}{1-\de_l p} > T$ and negative otherwise. So, when the benefit from the partner playing Trust is sufficiently small, the gift size increases in $D$. However, otherwise, the gift size decreases in the damages from the negotiating partner playing Distrust.

We now turn to the patience threshold that defines the high type. In the {concessions separating equilibrium} with no material value, we have $\frac{W}{T+D} = \de^{c}$, which increases in $W$ and decreases in $T$ and $D$. Notice it is not a function of $\delta_l$ or $p$.

The results for the patience threshold are more complex when concessions have future material value. First, recall that $\de^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$ where the denominator of the first term is simply $g^1$.

As in the case of no material value, the patience threshold increases in $W$: $\frac{\partial \delta^1}{\partial W} = \frac{p}{g^1} + p > 0$ because both $p$ and $g^1$ are strictly positive.

The patience threshold increases in $p$. That is, 
$$\frac{\partial \delta^1}{\partial p} = \frac{g^1 (W-D-T) - p(W-D-T)\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ W-T-D$$$$= (W-D-T)\left\{\frac{g^1  - p\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ 1\right\}=\frac{W-D-T	}{(g^1)^2}\left\{g^1  - p\frac{\partial g^1}{\partial p} + (g^1)^2\right\}$$
$$=\frac{W-D-T}{(g^1)^2}\left\{p(T+D)\left[-\de_l (1-\de_l) - \de_l D - \de_l p D(1-\de_l)\right]\right\} > 0.$$
We assume that $T > W - D$, so the fraction's numerator is positive, while the denominator is positive because it's a squared term. $p(T+D)$ is positive because all three variables are positive. Each term in the square brackets is negative. Therefore, the full expression is positive.

The patience threshold also increases in the low type's patience level $\de_l$. That is,
$$\frac{\partial \delta^1}{\partial \de_l} = \frac{g^1 \cdot 0 + p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} = \frac{p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} > 0.$$
The result holds because each term in the expression is positive.

In contrast, the patience threshold decreases in the benefit from the negotiating partner playing Trust, $T$. That is,
$$\frac{\partial \delta^1}{\partial T} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial T}}{(g^1)^2}-p = \frac{p}{(g^1)^2}\left\{ p(T+D-W) \frac{\partial g^1}{\partial T} - g^1 -(g^1)^2 \right\}$$
$$= \frac{p}{(g^1)^2}\left\{-(1-\de_l)W - (1- \de_l P)WD -2TD(1-\de_l)p \right\} < 0.$$
The result holds because $p$ and $g^1$ are positive, while each additive term in the curly braces is negative.

The result is more nuanced for $D$, the cost of the negotiating partner playing Distrust. The change in the patience threshold when $D$ changes is 
$$\frac{\partial \delta^1}{\partial D} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial D}}{(g^1)^2}+ (1-p).$$
If $T < \frac{1-\de_l}{1-\de_l p}$ so that $\frac{\partial g^1}{\partial D} > 0$, this expression is always negative. As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_l D(1-p)}{1-\de_l}$. When T grows even larger, the derivative remains negative as long as $W < \frac{(1-p)\de_l(T+D)^2}{T -1 + \de_l - \de_l p T}$.

\subsection{Material Value of Concessions can be Destroyed}
\emph{Proof of Lemma~\ref{lemma:efficiency}:}\\
The expected separation utility for the high type in the game with material value that can be destroyed is
$$p\frac{T+Teg_h}{1-\de_h} + (1-p)\frac{W-D-Deg_h}{1-\de_h} - (1-p)g_h.$$
The derivative with respect to $e$ is
$$\frac{1}{1-\de_h}\left\{pTg_h - (1-p)Dg_h)\right\}.$$
This is non-negative when $pT \geq (1-p)D$. High-type welfare is thus non-decreasing in $e$ when this condition is met. Thus, the largest admissible value of $e$, i.e., $e=1$, thus maximizes welfare when $pT \geq (1-p)D$.\footnote{If $pT = (1-p)D$, $e=1$ is not the unique maximizer but is still a maximizer.} \hfill $\blacksquare$\\
%\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function. It also holds for any monotone cost function.} 
\\
\emph{Proof of Lemma \ref{lemma:e-patient}:}\\
The proof is by contradiction. Suppose the patience threshold for the \emph{concessions separating equilibrium with inefficient gifts} is weakly larger than the patience threshold for the \emph{concessions separating equilibrium with efficient gifts}. Because low types have patience levels below the threshold, we have that 
\begin{equation}
	\de^c = \frac{W}{T+D} \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1> \de_l.
	\label{eq:cont}
\end{equation}
It follows directly that $W > \de_l(T+D)$. Because $\de_l < 1$, it is also true that $\frac{1-p}{1-\de_l p} < 1$. Combining this with the previous fact, we have
\begin{equation}
	W > \de_l(T+D) > \frac{\de_l(T+D)(1-p)}{1-\de_l p}.
	\label{eq:cont2}
\end{equation}
We invoke Expression~\ref{eq:cont2} below. First we go back to Expression~\ref{eq:cont}, simplifying and creating a common denominator for $\de^1$, we have
\begin{multline*}
	\frac{W}{T+D} \geq %\frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
	%+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = \\
	\frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{multline*}
Subtract $\frac{W}{T+D}$ from both sides to get
\begin{multline*}
	0 \geq \frac{-W(1-\de_l) + W\left(1-\de_l\right)-(D+T)\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT}{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
	+ \frac{(W-(D+T))(1-p) D + p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{multline*}
Canceling the first two terms as well as the third and last terms and then 
%\begin{multline*}
%	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
%	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 %T\right)}
%\end{multline*}
expanding and canceling the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
%\begin{multline*}
%	0 \geq \frac{-W\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
%	+ \frac{pW\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
%\end{multline*}
%Expand even more and then cancel out $(1-p)D\left(D +	 T\right)$ terms
\begin{equation*}
	0 \geq \frac{-W\left(1-\de_l\right)pT +W(1-p) D + pW\left(1-\de_l\right)\left(D +	 T\right) }{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{equation*}
Expanding once more and then canceling out the $W\left(1-\de_l\right)pT$ and $pWD$ terms
%\begin{equation*}
%	0 \geq \frac{W(1-p) D + pW(1-\de_l)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
%	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
%\end{equation*}
%Expand everything from the first fraction and cancel out $-pWD$ terms
\begin{equation*}
	0 \geq \frac{WD - \de_lpWD}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{equation*}
Combining this with the inequality in Expression~\ref{eq:cont2}, we arrive at
\begin{equation*}
	0 \geq \frac{WD(1- \de_lp)}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} > \frac{\frac{\de_l(T+D)(1-p)}{1-\de_l p}\left[D(1 - \de_lp)\right]}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{equation*}
To simplify, we have
\begin{equation*}
	0 > \frac{\de_l(T+D)(1-p)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = 0
\end{equation*}
We have arrived at a contradiction from Expression~\ref{eq:cont}, and therefore, it must be that 
\begin{equation}
	\frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 > \frac{W}{D+T}
\end{equation}
 \hfill $\blacksquare$

\subsection{Mediation}
\emph{Proof of Lemma \ref{lemma:med}:}\\
We show that the low type's incentive compatibility constraint cannot hold when the mediator specifies fully efficient gifts. The low type's incentive compatibility constraint in the mechanism $M$ is
$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h.$$

>>>>

Control of strategically valuable territory is often contested in both civil and interstate wars. Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide a military advantage in a future conflict. Following the 1992 war between Armenia and Azerbaijan over the disputed region of Nagorno-Karabakh, Armenia retained control of a significant amount of Azerbaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland. Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory. Thus, it might have been efficient in the mid-1990s for the Armenian/Karabakh side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence. However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor that connects Nagorno-Karabakh and Armenia. Azerbaijani control of the territory surrounding the corridor would empower Azerbaijan to seize military advantage in the future and cut off land travel between Nagorno-Karabakh and Armenia. The territory was not conceded, and the conflict persisted in a costly stalemate for almost twenty years until war broke out anew in 2020.

@@

\newpage
